Automating Verification of MPC Security

### 2023-06-09 popl24/hyperprop.tex
checkpoint

\subsection{A Sound Hyperproperty for Passive Security} The real/ideal
model can be hard to understand and passive security of protocols can
be difficult to prove, much less enforce automatically. Formulating
a hyperproperty that implies passive security can provide some
insights into the meaning of passive security, provide a connection
to the foundational theories we've discussed, and can provide
methodological support for proofs and even enforcement.

The intuition that passive security means that the protocol releases
no more information than what is released by the output suggests a
refinement of noninterference. Specifically, it suggests that in
passive secure protocols, the adversarial knowledge (in the Lecture
Notes 12 sense) obtained from the output does not change during
protocol execution, which otherwise should be noninterfering.  That
is, the set of low equivalent initial memories that can produce the
same output should generate the same distributions of adversarial
views. 
\begin{definition}[Noninterference Modulo Output]
  Given $H$, $C$, and a program $\prog$ with $\iov(\prog) = (S,V)$ and output
  view $x \in V$, we say that
  $\prog$ satisfies \emph{noninterference modulo output} iff for all
  $\store_1,\store_2 \in \mems(S)$:
  \begin{eqnarray*}
    & \store_1 =_C \store_2 \wedge
     (\margd{(\condd{\progd(\prog)}{\store_1})}{\{ x \}} =
     \margd{(\condd{\progd(\prog)}{\store_2})}{\{ x \}}) \\
    & \implies \\
    & \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}
  \end{eqnarray*}
\end{definition}
We can show, for example, that the 3-party xor protocol defined above
satisfies noninterference modulo output.

>>>>

\subsection{A Sound Hyperproperty for Passive Security}
The intuition that passive security means that the protocol releases
no more information than what is released by the output suggests a
refinement of noninterference. That is, the set of low equivalent
initial memories that can produce the same output should generate the
same distributions of adversarial views.
\begin{definition}[Noninterference Modulo Output]
  Given $H$, $C$, and a program $\prog$ with $\iov(\prog) = (S,V)$ and output
  view $x \in V$, we say that
  $\prog$ satisfies \emph{noninterference modulo output} iff for all
  $\store_1,\store_2 \in \mems(S)$:
  \begin{eqnarray*}
    & \store_1 =_C \store_2 \wedge
     (\margd{(\condd{\progd(\prog)}{\store_1})}{\{ x \}} =
     \margd{(\condd{\progd(\prog)}{\store_2})}{\{ x \}}) \\
    & \implies \\
    & \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}
  \end{eqnarray*}
\end{definition}
We can show, for example, that the 3-party xor protocol defined above
satisfies noninterference modulo output.
